---
title: "Enter indicator name here"
format: 
  html:
    embed-resources: true
author:
  - name: John Doe              # Enter name
    email: john.doe@example.no  # Enter email
    affiliations:
      - id: myID
        name: A Fictive Institute for Nature Research # Enter affiliations
  - name: Jane Doe              #  Enter subsequent authors like this, or remove if not relevant
    affiliations:
      - ref: myID               # To reuse affiliations referecen the id like this
date: April 10, 2024 # Enter date 
---

<!--# This is a template for how to document the indicator analyses. Make sure also to not change the order, or modify, the headers, unless you really need to. This is because it easier to read if all the indicators are presented using the same layout. If there is one header where you don't have anything to write, just leave the header as is, and dont write anything below it. If you are providing code, Be careful to annotate and comment on every step in the analysis.-->

# Indicator name

<!--# Replace 'indicator name' with your the actual indicator name -->

<br />

<!--# Load all you dependencies here -->

```{r setup}
#| include: false
library(knitr)
knitr::opts_chunk$set(echo = TRUE)
```

<!--# Use the IUCN Global Ecosystem Typology (GET) to describe which ecosystem the indicator belongs to. https://doi.org/10.2305/IUCN.CH.2020.13.en. If the indicator covers more than one category in the GET, choose the most prominent one here, and use the text to elaborate on the ecosystem affiliations. -->

```{r GET}
#| echo: false

Realm <- "Enter realm" # e.g. "Terrestrial"
Biome <- "Enter biome" #e.g. "Temperate-boreal forests and woodland"
EFG   <- "Enter EFG" # Ecosystem functional group, e.g. "Deciduous temperate forests"
```

<!--# Enter the ecosystem condition typology (ECT) class that your indicator best adhers too (10.3897/oneeco.6.e58218) -->

```{r ECT}
#| echo: false
ECT <- "Enter ECT" # e.g. "Structural state characteristic"
```

```{r, echo=F}
metaData <- data.frame(
  Realm,
  Biome,
  EFG, 
  "ECT class" = ECT)
knitr::kable(t(metaData))

```

<!--# Don't remove these three html lines -->

<br /> <br />

<hr />

<!--# Document you work below.  -->

## 1. Introduction

<!--# Describe the indicator in general terms. It is a good idea to include a bullet point list of the spesific steps in the workflow -->

## 2. About the underlying data

<!--# Describe the data you have used, it's origin, biases, avaiabilit ect.-->

### 2.1 Spatial and temporal resolution

<!--# Describe the temporal and spatial resolution of the data used-->

### 2.2 Original units

<!--# What are the original units for the most relevant  variables in the data-->

### 2.3 Additional comments about the dataset

<!--# Text here -->

## 3. Indicator properties

### 3.1. ECT

<!--# Describe the rationale for assigning the indicator to the ECT class -->

### 3.2. Ecosystem condition characteristic

<!--# Describe the ecosystem condition characteristic represneted in the indicator. See 10.3897/oneeco.6.e58218 for information on what these characteristics might be. -->

### 3.3. Other standards

<!--# Add text about other spesific standards, e.g. natinoal standards, and how the indicator relates to these -->

### 3.4. Collinearities with other indicators

<!--# Describe known collinearities with other metrices (indicators or variables) that could become problematic if they were also included in the same Ecosystem Condition Assessment as the indicator described here. -->

## 4. Reference condition and values

### 4. 1. Reference condition

<!--# Define the reference condition (or refer to where it is defined). Note the destinction between reference condition and reference values 10.3897/oneeco.5.e58216  -->

### 4. 2. Reference values, thresholds for defining *good ecological condition*, minimum and/or maximum values

<!--# Describe the different reference values here and the justification for using these -->

## 5. Uncertainties

<!--# Describe the main uncertainties or sources of error in the indicator or the underlying data. -->

## 6. References

<!--# You can add references manually or use a citation manager and add intext citations as with crossreferencing and hyperlinks. See https://quarto.org/docs/authoring/footnotes-and-citations.html -->

## 7. Analyses

### Data sets

<!-- Text here -->

#### Data set A

<!-- Text here -->

#### Data set B

<!-- Text here -->

#### Regions

<!-- In case you need to map the indicator value to regions, you can do that here. Remove this chapter if not relevant. -->

Importing a shape file with the regional delineation.

```{r}
#reg <- sf::st_read("data/regions.shp")
#st_crs(reg)
```

### Scaled indicator values

<!-- Text and analyses here -->

### Uncertainty

<!-- Text here -->

## Prepare export

<!-- Text here -->

### Eksport file (final product)

<!-- Export final file. Ideally a georeferenced shape or raster wit indicators values (raw and normalised), reference values and errors. -->
